### 2022-11-10 README.Rmd
Update readme
Update README.Rmd

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/isakro/assessing.sealevel.dating/master?urlpath=rstudio)

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials.

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/isakro/assessing.sealevel.dating/master?urlpath=rstudio)
[![R-CMD-check](https://github.com/isakro/assessing.sealevel.dating/actions/workflows/R-CMD-check.yml/badge.svg)](https://github.com/isakro/assessing.sealevel.dating/actions/workflows/R-CMD-check.yml)

@@

  - [:file\_folder: script](/analysis/script): R programming scripts for
  analysing the data. The derived data is loaded in the R Markdown source 
  document (below).
  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials.
